rang: Reconstructing reproducible R computational environments

### 2023-03-06 paper/paper.qmd
in

These solutions are better for prospective usage, i.e. using them now to ensure the reproducibility of the current research for future researchers. `rang` mostly targets retrospective usage, i.e. using `rang` to reconstruct historical R computational environments which have not been completely declared. One can think of `rang` as an archaeological tool. In the following examples, `rang` is used to enable the reproducibility of published literature.

@@

## Recover a removed R package

@@

@@

The Bioconductor package `Sushi` has been deprecated by the original authors and is removed from Bioconductor version 3.16 (2022-11-02). It is a data visualization tool for genomic data and was used in various online tutorials and papers, including the original paper announcing the package by the original authors [@phanstiel:2014:S].

# Generating a research compendium

>>>>

These solutions are better for prospective usage, i.e. using them now to ensure the reproducibility of the current research for future researchers. `rang` mostly targets retrospective usage, i.e. using `rang` to reconstruct historical R computational environments which have not been completely declared. One can think of `rang` as an archaeological tool. In Section 3, `rang` is used to enable the reproducibility of published literature.

@@

## Recover a removed R package: maxent

@@

## Recover a removed R package: ptproc

The R package `ptproc` was published as a paper in 2003 [@peng:2003:MDP]. But the package has been removed from CRAN for over a decade (at least). The only release on CRAN was on 2002-10-10. The package is still listed in the "Handling and Analyzing Spatio-Temporal Data" CRAN Task View. As of writing, the package is still downloadable from the original author's website [^peng].

Despite this over-a-decade removal, there is evidence that the package is still being sought for. As late as 2017, there are blog posts on how to install the long obsolete package on modern R [^blog].

[^peng]: https://www.biostat.jhsph.edu/~rpeng/software/

[^blog]: https://blog.mathandpencil.com/installing-ptproc-on-osx and https://tomaxent.com/2017/03/16/Installing-ptproc-on-Ubuntu-16-04-LTS/

@@

The Bioconductor package `Sushi` has been deprecated by the original authors and is removed from Bioconductor version 3.16 (2022-11-02). It is a data visualization tool for genomic data and was used in many online tutorials and papers, including the original paper announcing the package by the original authors [@phanstiel:2014:S].

# Producing a research compendium
